?????????????????

### 2022-11-24 article_1/Result1.tex
Export the images directly to the LaTeX images folder
Add random function with seeds and change variable names

%%%%%%%%%%%%%
\section{Aplication to Synthetic Data}

@@

>>>>

%%%%%%%%%%%%%
\begin{singlespace}
\section{Aplication to Synthetic Data}

\noindent{In order to test the efficiency of the proposed inversion method, we applied it to two sets of synthetic data contaminated by high and/or low frequency noise. }

\noindent{The first synthetic test is performed by generating a simple set of four spheres with similar magnetization intensity and radius, but completely different magnetization directions. Generating a data set contaminated by high frequency noise. In this simulation, the magnetization directions and magnetic moment intensity are directly compared with the initial input parameters. This first simplified test is basically done to investigate the efficiency of the inversions used for Euler positioning and magnetization parameters, thus being a validation of the methodology.}

\noindent{The second data set is data generated by a more complex model containing one hundred spheres with different radius and magnetization intensity, but magnetized in a similar direction within one standard deviation. This data set is corrupted by both low and high frequency noise. In this second application there is also validation using the comparison of the model data with the retrieved data. The complexity of this synthetic data seeks to more faithfully simulate the applicability of the proposed method to real SMM data.}

@@

\begin{figure}[hbpt]
\centering
\includegraphics[width=1.0\textwidth]{ComplexSynthetic.png}
\caption{a) Complex synthetic data contaminated with  both high and low frequencies noise. b) Individual sources window position (yellow squares) obtained with the blob detection algorithm applied on the total gradient map.}
\label{fig:ComplexSynthetic}
\end{figure}

\end{singlespace}

### 2022-11-24 article_1/input_par_table.tex
Add random function with seeds and change variable names

\begin{table}[htbp]
\caption{Initial position and magnetization parameters for each spherical source.}
\label{tab:ModelTab}
\resizebox{1.0\textwidth}{!}{
\tiny
\begin{tabular}{ccccccc}
\hline   
\rowcolor[HTML]{FFFFFF} 
\cellcolor[HTML]{FFFFFF}                         & \multicolumn{3}{c}{\cellcolor[HTML]{FFFFFF}Center coordinates}                    & \multicolumn{3}{c}{\cellcolor[HTML]{FFFFFF}Magnetization}     \\
\rowcolor[HTML]{FFFFFF} 
\multirow{-2}{*}{\cellcolor[HTML]{FFFFFF}Sphere} & Xc ($\mu m$) & Yc ($\mu m$) & Zc ($\mu m$) & m ($A \cdot m^2$) & D (\textdegree) & I (\textdegree) \\  \hline   
1                                                & 250.00                       & 250.00                       & 5.30                       & 8.70e-15               & -140.00                        & -30.00                 \\
\rowcolor[HTML]{FFFFFF} 
2                                                & 500.00                       & 500.00                       & 7.75                       & 7.63e-15               & 0.00                        & 62.00                 \\
3                                                & 750.00                       & 750.00                       & 8.50                       & 6.21e-15               & -70.00                        & -50.00                 \\
\rowcolor[HTML]{FFFFFF} 
4                                                & 200.00                       & 800.00                       & 10.00                       & 6.66e-15               & 125.00                        & 22.00                  \\ \hline                 
\end{tabular}
}
\end{table}

>>>>

\begin{table}[htbp]
\caption{Initial position and magnetization parameters for each spherical source.}
\label{tab:ModelTab}
\resizebox{1.0\textwidth}{!}{
\tiny
\begin{tabular}{ccccccc}
\hline   
\rowcolor[HTML]{FFFFFF} 
\cellcolor[HTML]{FFFFFF}                         & \multicolumn{3}{c}{\cellcolor[HTML]{FFFFFF}Center coordinates}                    & \multicolumn{3}{c}{\cellcolor[HTML]{FFFFFF}Magnetization}     \\
\rowcolor[HTML]{FFFFFF} 
\multirow{-2}{*}{\cellcolor[HTML]{FFFFFF}Sphere} & Xc ($\mu m$) & Yc ($\mu m$) & Zc ($\mu m$) & m ($A \cdot m^2$) & D (\textdegree) & I (\textdegree) \\  \hline   
1                                                & 250.00                       & 250.00                       & 5.30                       & -5.77e-15               & -140.00                        & -30.00                 \\
\rowcolor[HTML]{FFFFFF} 
2                                                & 500.00                       & 500.00                       & 7.75                       & -4.84e-15               & 0.00                        & 62.00                 \\
3                                                & 750.00                       & 750.00                       & 8.50                       & -4.35e-15               & -70.00                        & -50.00                 \\
\rowcolor[HTML]{FFFFFF} 
4                                                & 200.00                       & 800.00                       & 10.00                       & 3.58e-15               & 125.00                        & 22.00                  \\ \hline                 
\end{tabular}
}
\end{table}

### 2022-11-24 article_1/solution_par_table.tex
Add random function with seeds and change variable names

\begin{table}[htbp]
\caption{Positioning and magnetization parameters recovered with the inversion.}
\label{tab:InversionTab}
\resizebox{1.0\textwidth}{!}{
\begin{tabular}{ccccccc}
\hline   
\rowcolor[HTML]{FFFFFF} 
\cellcolor[HTML]{FFFFFF}                         & \multicolumn{3}{c}{\cellcolor[HTML]{FFFFFF}Center coordinates}                    & \multicolumn{3}{c}{\cellcolor[HTML]{FFFFFF}Magnetization}     \\
\rowcolor[HTML]{FFFFFF} 
\multirow{-2}{*}{\cellcolor[HTML]{FFFFFF}Sphere} & Xc ($\mu m$) & Yc ($\mu m$) & Zc ($\mu m$) & m ($A \cdot m^2$) & D (\textdegree) & I (\textdegree) \\  \hline   
1                                                & 250.03           & 249.99           & 5.33           & 8.75e-15  $\pm$  2.30e-17           & -140.04  $\pm$  0.19           & -29.76  $\pm$  0.13           \\
\rowcolor[HTML]{FFFFFF} 
2                                                & 499.96           & 500.05           & 7.70           & 7.60e-15  $\pm$  2.90e-17           & 1.17  $\pm$  0.61           & 62.50  $\pm$  0.27           \\
3                                                & 750.12           & 750.04           & 8.47           & 6.19e-15  $\pm$  3.52e-17           & -71.88  $\pm$  0.60           & -50.02  $\pm$  0.35           \\
\rowcolor[HTML]{FFFFFF} 
4                                                & 200.02           & 799.73           & 10.08           & 6.73e-15  $\pm$  5.05e-17           & 124.28  $\pm$  0.48           & 22.78  $\pm$  0.34           \\ \hline                 
\end{tabular}
}
\end{table}

>>>>

\begin{table}[htbp]
\caption{Positioning and magnetization parameters recovered with the inversion.}
\label{tab:InversionTab}
\resizebox{1.0\textwidth}{!}{
\begin{tabular}{ccccccc}
\hline   
\rowcolor[HTML]{FFFFFF} 
\cellcolor[HTML]{FFFFFF}                         & \multicolumn{3}{c}{\cellcolor[HTML]{FFFFFF}Center coordinates}                    & \multicolumn{3}{c}{\cellcolor[HTML]{FFFFFF}Magnetization}     \\
\rowcolor[HTML]{FFFFFF} 
\multirow{-2}{*}{\cellcolor[HTML]{FFFFFF}Sphere} & Xc ($\mu m$) & Yc ($\mu m$) & Zc ($\mu m$) & m ($A \cdot m^2$) & D (\textdegree) & I (\textdegree) \\  \hline   
1                                                & 250.07           & 250.04           & 5.36           & 8.83e-15  $\pm$  2.32e-17           & -140.03  $\pm$  0.18           & -29.45  $\pm$  0.13           \\
\rowcolor[HTML]{FFFFFF} 
2                                                & 500.00           & 500.01           & 7.71           & 7.57e-15  $\pm$  2.91e-17           & 0.23  $\pm$  0.60           & 61.79  $\pm$  0.27           \\
3                                                & 749.92           & 749.98           & 8.38           & 6.10e-15  $\pm$  3.46e-17           & -69.93  $\pm$  0.61           & -50.50  $\pm$  0.35           \\
\rowcolor[HTML]{FFFFFF} 
4                                                & 199.94           & 800.21           & 10.10           & 6.78e-15  $\pm$  5.09e-17           & 125.09  $\pm$  0.48           & 21.02  $\pm$  0.33           \\ \hline                 
\end{tabular}
}
\end{table}
